The Astropy Project

### 2017-12-06 main.tex
fix numfocus spelling

\acknowledgments

Who to thank?  numfocus, GSOC, Python Software Foundation

We thank the many web services that make developing and maintaining this package
feasible, such as GitHub, Travis CI, Appveyor, CircleCI, and Read the Docs.

>>>>

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students ofter turn into long-term contributors. We also
thank NumFOCUS and the Python Software Foundation for financial
support for various needs. Within the academic community, we thank
institutions that make it possible that astronomers and programmers on
their staff can contribute (part of) their time to the development of
\astropy projects. Furthermore, the \astropy packages would not exisit
in their current form without a number of webservices for code
hosting, continuous integration, and documentation; in particular,
\astropy heavily relies on GitHub, Travis CI, Appveyor, CircleCI, and
Read the Docs.  \astropypkg integrates with the SIMBAD database,
operated at CDS, Strasbourg, France.
